### 2020-11-19 Thesis-Chapter5-ThreatModel.tex
Clean up conclusion notes
Add argument that despite hackability, device EA is worth studying
Update threat model with hacking comments

\modelitem{\ac{EA} workarounds}{The user is capable of evading \ac{EA} mechanisms by encrypting data at a higher level
in the tech stack, e.g. by encrypting files before saving them to disk. This has already been discussed, and it out of
scope for evaluating the \ac{EA} system itself.}

@@

\begin{table}[h]
  \caption{Central Concepts in the \ldawmsr Proposal}
  \label{table-ldawmsr-concepts}
  \FlushLeft
  \small
  \begin{tabular}{ |l|p{6.4cm}|p{6.4cm}| }
    \hline
    \thead{Concept} & \thead{Implementation} & \thead{Outcome} \\ \hline
    Self-escrow
    & The Class key is escrowed in the device's Secure Enclave (or equivalent) using a write-only component; i.e.,
      software can update the key, but only an unexposed hardware interface can read it.
    & Since the Class key itself is being stored, there is no change to the security of the underlying cryptographic
      protocols. Physical possession and partial disassembly is required, which introduces practical barriers to mass
      surveillance.
    \\ \hline
    Time vaulting
    & The hardware interface responds to requests only after proof of sustained possession for a ``lockup period (e.g.,
      72 hours).''
    & The waiting period precludes ``sneak and peak'' attacks and further reduces the utility for mass surveillance.
    \\ \hline
    Authorization
    & After the lockup period, the requestor must provide evidence of authorization. This comes from a shared secret
      between the device and the manufacturer which can be obtained via legal process.
    & Physical possession is now not enough; law enforcement (or attackers) must provide this secret information to the
      device to unlock it.
    \\ \hline
    Transparency
    & In addition to the device disassembly, the escrow agent modifies the device (e.g., burns a fuse) when it has been
      unlocked. The device firmware detects this modification.
    & The device user has evidence that the device has been unlocked, preventing covert usage.
    \\ \hline
  \end{tabular}
\end{table}

@@

\ii{R2}, \ii{R3}, and \ii{R4} are repudiation attacks that belie the system's potential for abuse. The system relies on
legal process and cooperation of several parties. But what if the legal process involves secret courts, secret
investigations, and secrecy orders on the vendor \cite{shamsi_2011}? Destructive disassembly or the weaker hardware
transparency mechanism provide non-repudiation that the device was unlocked, if and only if one has physical access to
the device. Technically enforced transparency into device access requests and responses would grant non-repudiation at a
broader level. \ldawmsr does not include a mechanism for the feature, though other \ac{DAR} \ac{EA} proposals do
\cite{phan_key_2017} \cite{servan_schreiber_jje_2020}. Unfortunately, building this feature into a proposal makes it
potentially vulnerable the hawkish lawmaker, who may consider it an anti-feature.

>>>>

% FIXME: add current hacking techniques.

\modelitem{\ac{EA} workarounds}{The user is capable of evading \ac{EA} mechanisms by encrypting data at a higher level
in the tech stack, e.g. by encrypting files before saving them to disk. Additionally, investigators or attackers are
frequently capable of bypassing current lockout mechanisms. These have already been discussed, and it out of scope for
evaluating the \ac{EA} system itself.}

@@

\begin{table}[h]
  \caption{Central Concepts in the \ldawmsr Proposal}
  \label{table-ldawmsr-concepts}
  \FlushLeft
  \small
  \begin{tabular}{ |l|p{6.4cm}|p{6.4cm}| }
    \hline
    \thead{Concept} & \thead{Implementation} & \thead{Outcome} \\ \hline
    Self-escrow
    & The Class key is escrowed in encrypted form in the device's Secure Enclave (or equivalent) using a write-only
      component; i.e., software can update the key, but only an unexposed hardware interface can read it.
    & Since the Class key itself is being stored instead of the encryption scheme being changed, there is no change to
      the security of the underlying cryptographic protocols. Physical possession and partial disassembly is required,
      which introduces practical barriers to mass surveillance.
    \\ \hline
    Time vaulting
    & The hardware interface responds to requests only after proof of sustained possession for a ``lockup period (e.g.,
      72 hours).''
    & The waiting period precludes ``sneak and peak'' attacks and further reduces the utility for mass surveillance.
    \\ \hline
    Authorization
    & After the lockup period, the requestor must provide evidence of authorization. This comes from a shared secret
      between the device and the manufacturer which can be obtained via legal process.
    & Physical possession is now not enough; law enforcement (or attackers) must provide this secret information to the
      device to unlock it.
    \\ \hline
    Transparency
    & In addition to the device disassembly, the escrow agent modifies the device (e.g., burns a fuse) when it has been
      unlocked. The device firmware detects this modification.
    & The device user has evidence that the device has been unlocked, preventing covert usage.
    \\ \hline
  \end{tabular}
\end{table}

@@

\ii{R2}, \ii{R3}, and \ii{R4} are repudiation attacks that belie the system's potential for abuse. The system relies on
legal process and cooperation of several parties. But what if the legal process involves secret courts, secret
investigations, and secrecy orders on the vendor \cite{shamsi_2011}? Destructive disassembly or the weaker hardware
transparency mechanism provide non-repudiation that the device was unlocked, if and only if one has physical access to
the device. Technically enforced transparency into device access requests and responses would grant non-repudiation at a
broader level. \ldawmsr does not include a mechanism for the feature, though other \ac{DAR} \ac{EA} proposals do
\cite{phan_key_2017} \cite{servan_schreiber_jje_2020} \cite{goldwasser_public_2017}. Unfortunately, building this
feature into a proposal makes it potentially vulnerable the hawkish lawmaker, who may consider it an anti-feature.
